---
title: "Week 4 - Part 2"
author: "Hannah Brady"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Comparing city mileage of compact and suv cars

## Wrangling mpg data

In console viewed "mpg" data included with tidyverse.

Typed in ?mpg to get data description:
Fuel economy data from 1999 to 2008 for 38 popular models of cars

Create a subset of the two classes of cars that I am interested in: SUVs and compact cars

```{r}
compact_SUV <- mpg %>% 
  filter(class %in% c("compact", "suv"))
# could use unique funciton to verify that this worked and only kept compact and suv.
```

## Exploratory data visualization

### Exploratory histograms:
```{r}
ggplot(data = compact_SUV, aes(x = cty)) +
  geom_histogram(bins = 15) +
  facet_wrap(~class)
```

Thoughts on distribution: compact might be positively skewed (has an upper tail), suv looks pretty normal. No major red flags right now tho.

Can look a little closer tho using a quantile-quantile plot: the closer it is to linear, the closer your sample is to normally distributed.


### Exploratory quantil-quantile plot:
```{r}
ggplot(data = compact_SUV, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~class)
```

SUV is pretty close to linear. Compact is mostly linear except for upper tail. Similar to what we saw in histogram.

## Summary statistics

Find descriptive statistics

```{r}
car_stats <- compact_SUV %>% 
  group_by(class) %>% 
  summarize(mean_city = mean(cty),
            sd_city = sd(cty),
            n = n())
# Because n is > 30 and the central limit theorem, and we are only comparing means, we are not worried about whether or not or data is normally distributed.

car_stats
```


## 2-sample t-test

Create vectors creating observations for each sample (city gas mileage).
Filter our data to only include compact cars, and then pull data from cty column into a vector.

```{r}
compact_sample <- compact_SUV %>% 
  filter(class == "compact") %>% 
  pull(cty)
# If you did this with select() instead of pull, you would just end up with a 1-column data frame which is not what R wants. R wants a vector.

suv_sample <- compact_SUV %>% 
  filter(class == "suv") %>% 
  pull(cty)

t.test(x = compact_sample, suv_sample)
```
Differences in means is most important.
Null hypothesis is that these were drawn from populations with the same mean.
I am testing to see what the probability is of getting samples that are at least this different if that null hypothesis is true.
That's what the p-value tells you. 2.2e-16 is the smallest value that the t-test will report. Says there is close to a 0% chance that you could have randomly drawn samples with means that are at least this different from populations with the same mean.

Technically "there is a significant difference." <0.05






